Mathematical Formulation of Projection Problem

### 2025-03-08 docs/logbook.tex
Implemented signed volume function
Updated logbook

		Discussion with Steve: he'll ask IT, I will generate a simple example in Blender first.

@@

>>>>

		Discussion with Steve: he'll ask IT, I will generate a simple example in Blender first. Also code up the volume.

@@

	\begin{MeetingMinutes}{Mon 3/3/2025}{u7013004}
		Yesterday, I worked on the three Blender shapes. I have three equations which produce surfaces of volume 1.4 pi. The next step is to visualise these in Blender.

		I also tested the correctness of my signed volume function and it works correctly. As the mesh resolution increases, the volume approximates the true volume better and better.

		Going to write about my background.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Tue 4/3/2025}{u7013004}
		Made the mesh fairly high res, most of the volume is lost lengthways, so focus on upping resolution for that. Was able to render them.
	\end{MeetingMinutes}

	\begin{MeetingMinutes}{Wed 5/03/2025}{u7013004}
		Get the camera matrix.
		Get the Canny edge detector.
		After that, tidy up point cloud section and talk about how to perform surface reconstruction.
	\end{MeetingMinutes}
